In this paper, we have shown the importance of cost-constrained BO and formulated it as an instance of a constrained Markov decision process (CMDP).
We developed a rollout algorithm using a cheap exploration, expensive exploitation base policy that performed better than EI and EIpu on three hyperparameter optimization problems and a sensor set selection problem.  

These investigations into cost-constrained BO are promising and we believe there are many interesting directions for future work. 
First, the overhead of the optimizer itself should be taken into account, especially in the context of HPO. 
While the overhead is negligible when the cost of evaluating the black-box is large (e.g., when training neural networks), future work could explore simpler heuristics to lower the overhead of using rollouts.
Second, we believe approximate solutions to CMDPs other than rollout are worth investigating. 
State aggregation and state truncation are classical methods in the MDP setting that reduce the state space according to the transition probabilities and~\citet{altman1999constrained} extends them to the CMDP setting. 
Consequently, we may approximate our model through state aggregation and state truncation and compute an exact solution via linear programming.\looseness-1

Finally, we have limited our discussion to the sequential BO setting. 
However, cost-constrained BO becomes significantly more complex in the batch setting, when evaluations are performed in parallel.
This is another interesting topic for future work.

