
\section{\mfgpucbtwo: Bayesian Optimisation with Continuous Approximations}
\label{sec:mfgpucb}

% We now present our \mfgpucbtwos algorithm.
\mfgpucbtwos is a sequential strategy to select a domain point $\xt\in\Xcal$ and
fidelity $\zt\in\Zcal$ at time $t$ based on previous observations.
At time $t$, we will first
construct an upper confidence bound $\utilt$ for the function $\func$ we wish to optimise.
It takes the form,
\begin{align*}
\utilt(x) = \mutmo(x) + \betath \sigmatmo(x).
\numberthis
\label{eqn:mfucb}
\end{align*}
Recall from~\eqref{eqn:munsigman} that $\mutmo$ and $\sigmatmo$ are the posterior mean and
standard deviation of $\func$
% i.e. $\gunc$ restricted to $\zhf$,
using the observations from the previous $t-1$ time steps
at all fidelities, i.e. the entire $\Zcal\times\Xcal$ space.
% in the entire $\Zcal\times\Xcal$ space.
We will specify $\betat$ in theorems~\ref{thm:regret},~\ref{thm:main}. 
Following other UCB algorithms, our next point $\xt$ in the domain $\Xcal$ for evaluating
$\gunc$ is a maximiser of $\utilt$, i.e. $\xt \in \argmax_{x\in\Xcal} \utilt(x)$.

Next, we need to determine the fidelity $\zt\in\Zcal$ to query $g$.
For this we will first select a subset $\candfidelst(\xt)$ of $\Zcal$ as follows,
\begingroup
% \allowdisplaybreaks
\begin{align*}
&\candfidelst(\xt) = 
%   \{\zhf\}\cup\big
    \Big\{z\in\Zcal\,:\,\;\cost(z) < \cost(\zhf),
    \quad\tautmo(z,\xt) > \gamma(z), \\
%     &\hspace{1.25in}\inffunc(z) > \frac{\inffunc(\diamz) }{\betath}
%     &\hspace{1.25in}\inffunc(z) > \inffunc(\diamz) /\betath
    &\hspace{1.25in}\inffunc(z) > \betatmh\inffunc(\diamz)
      \Big\}, 
\numberthis\label{eqn:candfidelst}
\\[0.05in]
&\textrm{where } \quad\gamma(z) =\,
      \sqrt{\kernelscale}\;
        \inffunc(z)\;
        \bigg(\hspace{-0.02in}\frac{\cost(z)}{\cost(\zhf)}
%         \hspace{-0.02in}\bigg)^{\frac{1}{d+p+2}}
        \hspace{-0.02in}\bigg)^{q}
\,.
\end{align*}
\endgroup
Here, $\inffunc$ is the information gap function in~\eqref{eqn:inffunc} and
$\tautmo$ is the posterior standard deviation of $g$,
% and $p$ is the dimensionality of $\Zcal$.
and $p,d$ are the dimensionalities of $\Zcal,\Xcal$.
The exponent $q$ depends on the kernel. For the SE kernel, $q=1/(p+d+2)$.
% and $\diamz = \argmax_{z\in\Zcal}\|z-\zhf\|$.
% When $\Zcal=[0,1]^p$, $\diamz \leq \sqrt{p}$.
We filter out the fidelities we consider at time $t$ using three conditions as
specified above.
We elaborate on these conditions in more detail in Section~\ref{sec:fidelSelection}.
If $\candfidelst$ is not empty, we choose the cheapest fidelity in this
set, i.e. $\zt \in \argmin_{z\in\candfidelst}\cost(z)$.
If $\candfidelst$ is empty, we choose $\zt = \zhf$.
% Otherwise, we choose $\zt = \zhf$.

We have summarised the resulting procedure below in Algorithm~\ref{alg:mfgpucbtwo}.
An important advantage of \mfgpucbtwos is that it only requires specifying
the GP hyper-parameters for $\gunc$ such as the kernel $\kernel$.
In practice, this can be achieved by various effective heuristics such as maximising the
GP marginal likelihood or cross validation which are standard in most \bayos{} methods.
In contrast, \mfgpucbones of~\citet{kandasamy16mfbo} requires tuning several other
hyper-parameters.

\insertAlgoMFGPUCBTwo

\subsection{Fidelity Selection Criterion}
\label{sec:fidelSelection}

We will now provide an intuitive justification for the three conditions in the
 selection criterion for $\zt$, i.e., equation~\eqref{eqn:candfidelst}.
Recall that we query $\zhf$ only if $\candfidelst(\xt)$ is empty.
The first condition, $\cost(z) < \cost(\zhf)$ is fairly obvious;
since we wish to optimise $g(\zhf, \cdot)$ and since we are not rewarded for queries at
other fidelities, there
is no reason to consider fidelities that are more expensive than $\zhf$. 

The second condition, $\tautmo(z,\xt) > \gamma(z)$ says that we will only consider
fidelities where the posterior
variance is larger than a threshold
$\gamma(z) = \sqrt{\kernelscale}\inffunc(z)(\cost(z)/\cost(\zhf))^{1/(p+d+2)}$,
 which depends critically on two
quantities, the cost function $\cost$ and the information gap $\inffunc$. As a first step towards parsing this condition, observe that a reasonable multi-fidelity strategy should be inclined to query cheap
fidelities and learn about $\gunc$ before querying expensive fidelities.
Now notice that $\gamma(z)$ is monotonically increasing in $\cost(z)$, therefore, it becomes
easier for a cheap $z$ to satisfy $\tautmo(z,\xt)>\gamma(z)$ and be included in
$\candfidelst$ at time $t$. Moreover, since we choose $\zt$ to be the minimiser of $\cost$ in $\candfidelst$,
a cheaper fidelity will always be chosen over expensive ones if included in $\candfidelst$. 
Second, if a particular fidelity $z$ is far away from $\zhf$, it probably contains less information
about $g(\zhf,\cdot)$. Again, a reasonable multi-fidelity strategy should be discouraged from making such queries. 
This is precisely the role of the information gap $\inffunc$ which is increasing with
$\|z-\zhf\|$.
As $z$ moves away from $\zhf$, $\gamma(z)$ increases and
it becomes harder to satisfy $\tautmo(z,\xt)>\gamma(z)$.
Therefore, such a $z$ is less likely
to be included in $\candfidelst(\xt)$ and be considered for evaluation.
% Our analysis reveals that setting $\gamma$ as in~\eqref{eqn:candfidelst} allows us to
% trade off between the cost and information of the fidelities available to us; 
Our analysis reveals that setting $\gamma$ as in~\eqref{eqn:candfidelst} is a reasonable
trade off between cost and information in the approximations available to us; 
cheaper fidelities cost less, but provide less accurate information about the
function $\func$ we wish to optimise.
% 
% To provide more intuition for the second condition,
% recall that for the SE kernel, $\inffunc(z) \approx \|z-\zhf\|/\hz$ where $\hz$ is the
% bandwidth of $\phiz$.
% If $\gunc$ is very smooth across $\Zcal$, then the lower fidelities provide more
% information about $g(\zhf,\cdot)$.
% One should expect a reasonable strategy
% to exploit such information effectively as it is cheaper.
% Indeed, for fixed $\cost$, large $\hz$ reduces the threshold $\gamma(z)$ across the
% entire $\Zcal$, causing $\candfidelst$ to be nonempty and \mfgpucbtwos to
% consider lower fidelities extensively before proceeding to $\zhf$.
% On the other hand, if $\hz$ is small and $\gunc$ is not smooth across $\Zcal$, the
% threshold $\gamma(z)$ will be large for all $z$. 
% Then $\candfidelst$ vanishes fast and the algorithm will quickly 
% skip lower fidelities and proceed to $\zhf$.
% We demonstrate this behaviour via an example in Section~\ref{sec:experiments}.
%Thus, this behaviour of \mfgpucbtwos is sensible in the SE kernel case. %we are repeating this too often
It is worth noting that the second condition is similar in
spirit to~\citet{kandasamy16mfbo} who proceed from a lower to higher
fidelity only when the lower fidelity variance is smaller than a threshold.
However, while they treat the threshold as a hyper-parameter, we are able to explicitly
specify theoretically motivated values.


% Finally, the third condition in~\eqref{eqn:candfidelst} says we should only
% consider fidelities $z$ satisfying $\inffunc(z) > \inffunc(\diamz)/\betath$. 
% says that we should only pick
% fidelities where the information gap $\inffunc$ is large. 
The third condition in~\eqref{eqn:candfidelst} is
$\inffunc(z) > \inffunc(\diamz)/\betath$. 
Since $\inffunc$ is increasing as we move away from
$\zhf$, it says we should exclude fidelities inside a (small) neighbourhood of $\zhf$.
Recall that if $\candfidelst$ is empty, \boca{} will choose $\zhf$ by default.
But when it is not empty, we want to prevent situations where we get
arbitrarily close to
$\zhf$ but not actually query \emph{at} $\zhf$.
Such pathologies can occur when we are dealing with a continuum of fidelities and
this condition forces \bocas to pick $\zhf$ instead of querying very close to it.
Observe that since $\betat$ is increasing with $t$, this neighborhood is shrinking with time
and therefore the algorithm will eventually have the opportunity to evaluate fidelities
close to $\zhf$.
% Next, we describe our theoretical results.

\input{theory}


% \subsection{Practical Implementation}
% \label{sec:implementation}


% \subsection{Beyond Continuous Fidelity spaces and Domains}
% \label{sec:extensions}

\textbf{Extensions:}
While we have focused on continuous $\Zcal$ due to their wide ranging
practical applications, many of the ideas here can be extended to other settings.
If $\Zcal$ is a discrete subset of $[0,1]^p$ our work extends straightforwardly.
We reiterate that this will \emph{not} be the same as the finite fidelity
\mfgpucbones algorithm as the assumptions are significantly different.
In particular,~\citet{kandasamy16mfbo} are not able to effectively share
information across fidelities as we do.
We also believe that Algorithm~\ref{alg:mfgpucbtwo} can be extended to arbitrary fidelity
spaces $\Zcal$ given that a kernel can be defined on $\Zcal$.
% Another avenue for future work would be to study different choices for
% $\Zcal$ kernel where 
% These questions are left for future work.
% In particular when $\Xcal$ is a discrete set, the analysis can be extended in a
% straightforward way.
Our results can also be extended to discrete domains $\Xcal$
and various kernels for $\phix$ by adopting techniques 
from~\citet{srinivas10gpbandits}.
As with most nonparametric models, \mfgpucbtwos scales poorly with
dimension due to the dependence on $\IGn$.
For this reason, we also confine our experiments to small $p,d$.
This could be addressed by assuming additional structure on
$\func,\gunc$~\citep{djolonga13highdimbandits,kandasamy15addBO}.


